Appendix S1: Supporting Tables and Figures

### 2022-01-20 ms/SI.Rmd
Fix CSL file for SI

---
title: "Appendix S1: Supporting Tables and Figures"
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: default
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "apa-6th-edition.csl"]
header-includes: 
  - \usepackage{float} # keep figures from floating away
  - \usepackage{booktabs} # need for kable tables
  - \usepackage{colortbl} # need for kable tables
  - \makeatletter\renewcommand*{\fps@figure}{H}\makeatother # keep figures from floating away
  - \usepackage{fancyhdr} # enable header
  - \pagestyle{fancy}  # enable header
  - \fancypagestyle{plain}{\pagestyle{fancy}} # show header on first page
  - \renewcommand{\headrulewidth}{0pt} # delete line beneath header
  - \fancyhead[RE,RO]{Nitta \textit{et al}. Spatial phy. of Japanese ferns Appendix S1} # add header on right side
  - \fancyhead[LO,LE]{} # suppress automatic section header on left side
  - \cfoot{\thepage} # footer
editor_options: 
  chunk_output_type: console
params:
  doc_type: pdf
# nocite: | 
---

@@

```{r load-data-si, cache = FALSE}
tar_load(c(
  "japan_shp",
  "inext_res",
  "redundancy_by_res",
  "redundancy_summary",
  "biodiv_ferns_spatial",
  "biodiv_ferns_endemic_spatial",
  "k_taxonomy",
  "k_phylogeny",
  "traits_nmds",
  "ppgi",
  "phy_sig_results",
  "binary_sig_results",
  "lrt_results",
  "japan_shp",
  "morans_i",
  "t_test_results",
  "aic_env_repro",
  "comm_ferns",
  "repro_data",
  "japan_pterido_tree",
  "model_fits_not_ult",
  "biodiv_ferns_cent",
  "protected_areas",
  "deer_range",
  "biodiv_ferns_spatial_lumped",
  "bioregion_cutoff"
))
```

```{r load-captions}
# Source captions numbers from MS
# 
# So that caption numbers are in order of appearance in MS

>>>>

---
title: "Appendix S1: Supporting Tables and Figures"
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: default
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "american-journal-of-botany.csl"]
header-includes: 
  - \usepackage{float} # keep figures from floating away
  - \usepackage{booktabs} # need for kable tables
  - \usepackage{colortbl} # need for kable tables
  - \makeatletter\renewcommand*{\fps@figure}{H}\makeatother # keep figures from floating away
  - \usepackage{fancyhdr} # enable header
  - \pagestyle{fancy}  # enable header
  - \fancypagestyle{plain}{\pagestyle{fancy}} # show header on first page
  - \renewcommand{\headrulewidth}{0pt} # delete line beneath header
  - \fancyhead[RE,RO]{Nitta \textit{et al}. Spatial phy. of Japanese ferns Appendix S1} # add header on right side
  - \fancyhead[LO,LE]{} # suppress automatic section header on left side
  - \cfoot{\thepage} # footer
editor_options: 
  chunk_output_type: console
params:
  doc_type: pdf
# nocite: | 
---

@@

```{r load-data-si, cache = FALSE}
tar_load(c(
  "japan_shp",
  "inext_res",
  "redundancy_by_res",
  "redundancy_summary",
  "biodiv_ferns_spatial",
  "biodiv_ferns_endemic_spatial",
  "k_taxonomy",
  "k_phylogeny",
  "traits_nmds",
  "ppgi",
  "phy_sig_results",
  "binary_sig_results",
  "lrt_results",
  "japan_shp",
  "morans_i",
  "t_test_results",
  "aic_env_repro",
  "comm_ferns",
  "repro_data",
  "japan_pterido_tree",
  "model_fits_not_ult",
  "biodiv_ferns_cent",
  "protected_areas",
  "deer_range",
  "biodiv_ferns_spatial_lumped",
  "bioregion_cutoff",
  "ms_functions"
))
```

```{r load-captions, cache = FALSE}
# Source captions numbers from MS
# 
# So that caption numbers are in order of appearance in MS
